\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}

\begin{document}

\title{Sustainable Crop and Organic Fertilizer Recommendation System}

\author{
    \IEEEauthorblockN{Pavan M. Magadum, Prof. Vasantha S and Prof. Rajesh Kumar}
    \IEEEauthorblockA{Department of Master of Computer Applications\\
    Sir M. Visvesvaraya Institute of Technology\\
    Visvesvaraya Technological University, Bangalore, India\\
    (pavanmagadum8, vasantha.s, rajesh.k)@sirmvit.edu}
}

\maketitle

\begin{abstract}
This is a demo showing how three authors appear side by side in IEEE conference paper format. The authors will be displayed horizontally across the page with proper spacing and alignment.
\end{abstract}

\begin{IEEEkeywords}
IEEE, LaTeX, Three Authors, Conference Paper, Demo
\end{IEEEkeywords}

\section{Introduction}
This is a demonstration document showing the three-author layout for IEEE conference papers. When you compile this document in Overleaf or any LaTeX editor, you will see all three authors displayed side by side below the title.

\section{Author Block Structure}
Each author block uses:
\begin{itemize}
    \item \texttt{\textbackslash IEEEauthorblockN\{\}} for the author name
    \item \texttt{\textbackslash IEEEauthorblockA\{\}} for affiliation details
    \item \texttt{\textbackslash and} to separate authors and place them side by side
\end{itemize}

\section{Conclusion}
This demo shows the proper IEEE format for three authors. Simply replace the names, affiliations, and email addresses with your actual information.

\begin{thebibliography}{00}
\bibitem{ieee}
IEEE, ``IEEE Conference Template,'' 2024.
\end{thebibliography}

\end{document}
